Carbonate chemistry at Ny-Ålesund

### 2023-06-03 awipev-CO2.Rmd
New fig air-sea for manuscript

size_point <- 1.5 # size of data points
alpha <- 1 #transparency
size_labs <- 14 # font size labels
# temp_insitu_11m
ts_air_sea_corr <- air_sea_long %>%
  ggplot(aes(x = montht, y = f_air_sea / 1000, fill = Formulation), na.rm = TRUE) +
  geom_col(alpha = alpha, position = "dodge") +
  lims(y = c(-3, 0)) +
  geom_hline(yintercept = 0, size = 0.5) +
  labs(title=NULL, 
       x="Month", 
       y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)", bold = TRUE)) +
  scale_fill_discrete(name = "", labels = c("Dobashi & Ho (2023)", "Ho et al. (2006)")) +
  Mytheme(size_labs = size_labs) +
  theme(aspect.ratio=0.5,
        plot.margin = margin(t = -10, r = 0.2, b = -10, l = 0.2, unit = "cm"),
        axis.title.x = element_text(face = "bold", size = 14),
        axis.title.y = element_text(face = "bold", size = 14),
        axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14)
        ) 
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_air_sea_corr
ggsave(filename = "figures/ts_air_sea_corr.png", plot = ts_air_sea_corr, width = 20, units = "cm")
#ggsave(filename = "figures/essd/ts_air_sea_corr.pdf", plot = ts_air_sea_corr, units = "cm")

@@

```{r monthly air-sea for paper, echo=FALSE, message= FALSE, warning=FALSE}
ts_air_sea <- air_sea_long %>%
  ggplot(aes(x = montht, y = f_air_sea / 1000, fill = Formulation), na.rm = TRUE) +
  geom_col(alpha = alpha, position = "dodge") +
  lims(y = c(-3, 0)) +
  geom_hline(yintercept = 0, size = 0.5) +
  labs(title=NULL, 
       x="Month", 
       y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)", bold = TRUE)) +
  scale_fill_discrete(name = "", labels = c("Dobashi & Ho (2023)", "Ho et al. (2006)")) +
  Mytheme(size_labs = size_labs) +
  theme(aspect.ratio=0.5,
        plot.margin = margin(t = -10, r = 0.2, b = -10, l = 0.2, unit = "cm"),
        axis.title.x = element_text(face = "bold", size = 14),
        axis.title.y = element_text(face = "bold", size = 14),
        axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14)
        ) 
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_air_sea_corr
ggsave(filename = "figures/essd/ts_air_sea.pdf", plot = ts_air_sea_corr, units = "cm")
```

>>>>

size_point <- 1.5 # size of data points
alpha <- 1 #transparency
size_labs <- 14 # font size labels
ts_air_sea_corr <- air_sea_long %>%
  ggplot(aes(x = montht, y = f_air_sea / 1000, fill = Formulation), na.rm = TRUE) +
  geom_col(alpha = alpha, position = "dodge") +
  lims(y = c(-3, 0)) +
  geom_hline(yintercept = 0, size = 0.5) +
  labs(title=NULL, 
       x="Month", 
       y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)", bold = TRUE)) +
  scale_fill_discrete(name = "", labels = c("Dobashi & Ho (2023)", "Ho et al. (2006)")) +
  Mytheme(size_labs = size_labs) +
  theme(aspect.ratio=0.5,
        plot.margin = margin(t = -10, r = 0.2, b = -10, l = 0.2, unit = "cm"),
        axis.title.x = element_text(face = "bold", size = 14),
        axis.title.y = element_text(face = "bold", size = 14),
        axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14)
        ) 
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_air_sea_corr
ggsave(filename = "figures/ts_air_sea_corr.png", plot = ts_air_sea_corr, width = 20, units = "cm")
#ggsave(filename = "figures/essd/ts_air_sea_corr.pdf", plot = ts_air_sea_corr, units = "cm")

@@

```{r monthly air-sea for paper, echo=FALSE, message= FALSE, warning=FALSE}
size_point <- 1.5 # size of data points
alpha <- 1 #transparency
size_labs <- 14 # font size labels
ts_air_sea <- air_sea_long %>%
  ggplot(aes(x = montht, y = f_air_sea / 1000, fill = Formulation), na.rm = TRUE) +
  geom_col(alpha = alpha, position = "dodge") +
  lims(y = c(-3, 0)) +
  geom_hline(yintercept = 0, size = 0.5) +
  labs(title=NULL, 
       x="Month", 
       y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)", bold = TRUE)) +
  scale_fill_discrete(name = "", labels = c("Dobashi & Ho (2023)", "Ho et al. (2006)")) +
    Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        #axis.text.x=element_blank(),
        #axis.text.y=element_blank(),
        axis.title.x = element_text(face = "bold", size = size_labs),
        #axis.label.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5),
        aspect.ratio=0.5,
        plot.margin = margin(t = 0, r = 0.2, b = 0, l = 0.2, unit = "cm"),
        legend.position = "top",
        legend.text = element_text(size=size_labs),
        legend.background = element_rect("transparent")
        ) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_air_sea
ggsave(filename = "figures/essd/ts_air_sea.pdf", plot = ts_air_sea, width = 15, height = 10, units = "cm")
```
